\emph{Gaia} DR2 identifies VFTS 682 as the most massive runaway star known to date

### 2018-05-15 VFTS682.tex
errorbar on positions is wrong! units
Jorick's initials

\author{M.~Renzo$^{1}$, S.~E.~de~Mink$^{1}$, D.~J.~Lennon$^{2}$,
  R.~P.~van~der~Marel$^{3,4}$, J. Bestenlehner$^{5}$, V.~H\'enault-Brunet$^{6}$, S.~Justham$^{7,8}$, F.~R.~Schneider$^9$, J.~Vink$^{10}$}

@@

\begin{table}[t]
\begin{center}
    \caption{Astrometric parameters for VFTS 682. }
  \begin{tabular}{l|c|c}
  \tableline
\tableline
    Parameter & Value & Source\\ 
    \tableline
    RA \hfill[degree] &  \phantom{-}84.73 $\pm$  0.03 & \multirow{4}{*}{\emph{Gaia} DR2}\\
    DEC \hfill [degree] & -69.07 $\pm$  0.05  & \\
    $\mu_\mathrm{RA}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & \phantom{-0}1.84 $\pm$ 0.07 & \\
    $\mu_\mathrm{DEC}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & \phantom{-0}0.78 $\pm$ 0.08& \\
    $\delta v_\mathrm{rad}$  \hfill[$\kms$] & \phantom{-0}30 $\pm$ 20 & \cite{bestenlehner:11}\\
\tableline
  \end{tabular}
  \tablecomments{We truncate the decimals on RA and DEC and the
    relative errors for the purpose
    of display. Readers are encouraged to consult the \emph{Gaia} DR2 catalog
  for accurate values.}
    \end{center}
  \label{tab:vfts682}
\end{table}

>>>>

\author{M.~Renzo$^{1}$, S.~E.~de~Mink$^{1}$, D.~J.~Lennon$^{2}$,
  R.~P.~van~der~Marel$^{3,4}$, J. Bestenlehner$^{5}$,
  A.~de~Koter$^{1}$, V.~H\'enault-Brunet$^{6}$, S.~Justham$^{7,8}$,
  I.~Platais$^{9}$, F.~R.~Schneider$^{10}$, J.~S.~Vink$^{11}$}

@@

\begin{table}[t]
\begin{center}
    \caption{Astrometric parameters for VFTS 682. }
  \begin{tabular}{l|c|c}
  \tableline
\tableline
    Parameter & Value & Source\\ 
    \tableline
    RA \hfill[degree] &  \phantom{-}84.73 $\pm$  0.03 & \multirow{4}{*}{\emph{Gaia} DR2}\\
    DEC \hfill [degree] & -69.07 $\pm$  0.05  & \\
    $\mu_\mathrm{RA}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & \phantom{-0}1.84 $\pm$ 0.07 & \\
    $\mu_\mathrm{DEC}$  \hfill[$\mathrm{mas\ yr^{-1}}$] & \phantom{-0}0.78 $\pm$ 0.08& \\
    $\delta v_\mathrm{rad}$  \hfill[$\kms$] & \phantom{-0}30 $\pm$ 20 & \cite{bestenlehner:11}\\
\tableline
  \end{tabular}
  \tablecomments{\todo{the error on position is in milliarcsec, not
      degrees! Fix this, Roeland is right!}}
    \end{center}
  \label{tab:vfts682}
\end{table}
